\chapter{Objectives}\label{sec:objectives}
%\cbstart
%This chapter is organized exclusively for charitable, educational, and scientific purposes under section 501(c)(3) of the Internal Revenue Code, or corresponding Section of any future federal tax code.
%\cbend
\section{}
The objectives of the Beta Epsilon of \hkn are:

%\begin{compactenum}[1.]\itemsep4pt

%\let\oldenumi\labelenumii
%\renewcommand{\labelenumii}{\arabic{enumii}.}
\begin{enumsubsection}

\itemnotoc To uphold the purposes and ideals of \hkn as articulated by IEEE-HKN.

\itemnotoc To promote and encourage excellence in electrical engineering, computer engineering, computer science, and related fields for the betterment of fellow students, the department, the University, and the public at large.

\itemnotoc To foster a spirit of respect and cooperation between students and the faculty of the University of Michigan.
\itemnotoc To cooperate with and support the activities of the local IEEE student branch.
\itemnotoc To cooperate and collaborate with other student organizations on the campus with regards to community service, service to the University, and facilitation of inter-organizational networking.
\itemnotoc To cooperate and collaborate with other chapters of \hkn with regards to contributing to the broader organization, improving the chapters' communities, and facilitating networking between \hkn members.
\itemnotoc To uphold the motto, creed, and objectives of the Association.

\end{enumsubsection}

\section{Non-Discrimination}
\hkn is committed to a policy of equal opportunity for all persons and does not discriminate on the basis of race, color, national origin, age, marital status, sex, sexual orientation, gender identity, gender expression, disability, religion, height, weight, or veteran status in its membership or activities unless permitted by university policy for gender specific organizations.

