\documentclass[incorporation,proposal,withoutpreface,withoutoptional,11pt,final]{bylaws}
\usepackage[color]{changebar}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{url}
\organization{Eta Kappa Nu -- Beta Epsilon Chapter}
%\orglogo{HKNcrest}
\adoptiondate{19 March 2018}
\chapteramendmentdate{19 March 2018}
\newcommand{\hkn}{IEEE-HKN }

\newcommand{\removed}[1]{\cbstart\removedfragile{#1}\cbend{}}
\newcommand{\removedfragile}[1]{{\color{red}{#1}}{}}
\newcommand{\added}[1]{\cbstart\addedfragile{#1}\cbend{}}
\newcommand{\addedfragile}[1]{{\color{green!50!black}{#1}}{}}
\newcommand{\changed}[2]{\added{#1}\removed{#2}}

\begin{document}
\cbcolor{red}
\frontmatter
\maketitle
\setcounter{tocdepth}{0}
%\tableofcontents
%\newpage
\mainmatter
\chapter*{Preface}\addcontentsline{toc}{chapter}{Preface}
The key words ``MUST'', ``MUST NOT'', ``REQUIRED'', ``SHALL'', ``SHALL NOT'', ``SHOULD'', ``SHOULD NOT'', ``RECOMMENDED'',  ``MAY'', and ``OPTIONAL'' in this and any subordinate documents are to be interpreted as described in \href{http://www.ietf.org/rfc/rfc2119.txt}{RFC 2119}.
%\input{charter.tex}
%\input{objective.tex}
%\input{bylaws.tex}
%\input{membership.tex} % Includes all types of membership, candidates, and officers
%\input{advisors.tex}
%\input{trustees.tex}
%\input{compliance.tex}

%\input{amendments.tex}

\chapter{Name}
\section{} The name of the corporation shall be Eta Kappa Nu, Beta Epsilon Chapter, Inc.

\chapter{Purpose}
\section{} The purposes for which the corporation is formed are to maintain an activity club for exceptional students engaged in the IEEE--Eta Kappa Nu honor society at the University of Michigan--Ann Arbor with a focus on students student electrical engineering, computer engineering, and computer science.
The activity club will foster ethical behavior and community service through regular meetings, social events, fundraising activities, and service projects.

\chapter{Governance}
\section{} The corporation is formed upon a nonstock basis.

\section{} The corporation has no real or personal property assets.

\section{} The corporation is to be financed via charitable fundraising, membership dues, and selling goods and services.

\section{} The corporation is formed on a directorship basis.

\chapter{Registered Agent}
\section{} The resident agent at the registered office is Kyle Lady.

\section{} The address of the registered office in Michigan is 618 S. Main St., Ann Arbor, MI 48104.

\chapter{Incorporators}
The names and addresses of the incorporators are as follows:
\section{} Located at 1301 Beal Ave., Ann Arbor, MI 48109:
\begin{itemize}
	\item Michael Benson
	\item Carson Boden
	\item Paul Giessner
	\item Ian Hiskens
	\item Abhinav Reddy
	\item Ankit Shah
	\item Alexandria Shand
\end{itemize}

\section{} Located at 618 S. Main St., Ann Arbor, MI 48104:
\begin{itemize}
	\item Kyle Lady
\end{itemize}

\chapter{Corporate Bylaws}
Eta Kappa Nu, Beta Epsilon Chapter, Inc.\@ shall maintain corporate bylaws in the form of the Chapter Constitution. 
Directives and prerogatives contained within the Chapter Constitution shall have the force and effect as if contained within these Articles.
All conflicts between the Chapter Constitution and these Articles shall be resolved in favor of these Articles.

\chapter{Board of Directors}
The Chapter Constitution shall define an ``Advisory Board''. 
The Board of Directors of Eta Kappa Nu, Beta Epsilon Chapter, Inc.\@ shall consist of the members of said Advisory Board and shall update its membership as the Advisory Board membership changes.
The president, vice president, and secretary of the Board of Directors shall be those individuals holding the corresponding titles on the Advisory Board.
The treasurer of the Board of Directors shall be the individual holding the title of Chapter Financial Advisor.                                                                                                                                                                                                                  

\chapter*{Signatories} \addcontentsline{toc}{chapter}{Signatories}

We, the incorporators, sign our names this nineteenth day of March 2018:
\vspace{0.5in}

\vspace{0.5in}
\noindent Michael Benson

\vspace{0.5in}
\noindent Carson Boden

\vspace{0.5in}
\noindent Paul Giessner

\vspace{0.5in}
\noindent Ian Hiskens

\vspace{0.5in}
\noindent Kyle Lady

\vspace{0.5in}
\noindent Abhinav Reddy

\vspace{0.5in}
\noindent Ankit Shah

\vspace{0.5in}
\noindent Alexandria Shand


\vspace{0.75in}
\noindent Preparer's name: Kyle Lady

\noindent Business Telephone Number: 517-937-8238

\end{document}
